Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-06 doc/RMD/pop-diff.Rmd
change direction of viridis palette

```{r fig.width = 10, fig.height = 6}
LDS <- bind_cols(Population = region.dapc$grp, as.data.frame(region.dapc$ind.coord)) %>%
  as_tibble()
LDS_pop <- LDS %>% 
  group_by(Population) %>% 
  summarize_all(mean) %>%
  rename_all(function(x) gsub("LD", "mean", x))
LDS <- full_join(LDS, LDS_pop)
LDS_PLOT <- ggplot(LDS, aes(x = LD1, y = LD2, color = Population)) + 
  geom_point(aes(fill = Population), alpha = 0.5, pch = 21, color = "black") +
  geom_segment(aes(x = mean1, y = mean2, xend = LD1, yend = LD2), alpha = 0.5) +
  stat_ellipse(type = "norm", level = 0.66, alpha = 0.75) + 
  ggrepel::geom_label_repel(aes(x = mean1, y = mean2, label = Population), 
                            data = LDS_pop, show.legend = FALSE, color = "black") +
  theme_bw() +  
  theme(aspect.ratio = 1/1.618) +
  theme(legend.position = "bottom") +
  theme(axis.text = element_blank()) + 
  theme(axis.title = element_blank()) + 
  theme(axis.ticks = element_blank()) + 
  viridis::scale_color_viridis(discrete = TRUE) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  scale_y_continuous(breaks = 0) + 
  scale_x_continuous(breaks = 0) + 
  theme(panel.background = element_rect(fill = "grey95")) +
  theme(panel.grid.major = element_line(color = "black"))
LDS_PLOT
LDS_PLOT + facet_wrap(~Population)
```

>>>>

```{r fig.width = 10, fig.height = 6}
LDS <- bind_cols(Population = region.dapc$grp, as.data.frame(region.dapc$ind.coord)) %>%
  as_tibble()
LDS_pop <- LDS %>% 
  group_by(Population) %>% 
  summarize_all(mean) %>%
  rename_all(function(x) gsub("LD", "mean", x))
LDS <- full_join(LDS, LDS_pop)
LDS_PLOT <- ggplot(LDS, aes(x = LD1, y = LD2, color = Population)) + 
  geom_point(aes(fill = Population), alpha = 0.5, pch = 21, color = "black") +
  geom_segment(aes(x = mean1, y = mean2, xend = LD1, yend = LD2), alpha = 0.5) +
  stat_ellipse(type = "norm", level = 0.66, alpha = 0.75) + 
  ggrepel::geom_label_repel(aes(x = mean1, y = mean2, label = Population), 
                            data = LDS_pop, show.legend = FALSE, color = "black") +
  theme_bw() +  
  theme(aspect.ratio = 1/1.618) +
  theme(legend.position = "bottom") +
  theme(axis.text = element_blank()) + 
  theme(axis.title = element_blank()) + 
  theme(axis.ticks = element_blank()) + 
  viridis::scale_color_viridis(discrete = TRUE, direction = -1) +
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_y_continuous(breaks = 0) + 
  scale_x_continuous(breaks = 0) + 
  theme(panel.background = element_rect(fill = "grey95")) +
  theme(panel.grid.major = element_line(color = "black"))
LDS_PLOT
LDS_PLOT + facet_wrap(~Population)
```

### 2017-07-06 doc/manuscript/manuscript.Rmd
change direction of viridis palette

![
Discriminant Analysis on regions showing that Mexico is differentiated from other populations. 
**(a)** Mean population assignment (horizontal axis) probability (vertical axis) for all populations with N > 10 (facets).
All values sum to one.
**(b)** Scatter plot of first two components from DAPC.
Points represent observed individuals connected to the population centroids with ellipses representing a 66% confidence interval for a normal distribution. 
](../../results/figures/publication/DAPC.pdf){#DAPC width=100%}

@@

Table: (\#tab:iatab) Genotypic diversity and Linkage Disequilibrium summary for geographic populations arranged by abundance after clone-correction by a hierarchy of Region/Source/Host/Year. 
Pop = Population, N = number of individuals (number of MLG in parentheses), 
eMLG = expected number of MLGs based on rarefaction at 10 individuals (standard error in parentheses), 
H = Shannon-Weiner Index, G = Stoddardt and Taylor's Index, 
$\lambda$ = Simpson's Index, 
*h* = Nei's 1978 gene diversity, 
$I_A$ = the index of association, 
$\bar{r}_d$ = standardized index of association. 
P-value symbols: \* = 0.001, ~ = $\leq 0.05$.

>>>>

![
Discriminant Analysis on regions showing that Mexico is differentiated from other populations. 
**(a)** Mean population assignment (horizontal axis) probability (vertical axis) for all populations with N > 10 (facets).
Numbers next to source populations indicate population size.
All values sum to one.
**(b)** Scatter plot of first two components from DAPC.
Points represent observed individuals connected to the population centroids with ellipses representing a 66% confidence interval for a normal distribution. 
](../../results/figures/publication/DAPC.pdf){#DAPC width=100%}

@@

Table: (\#tab:iatab) Genotypic diversity and Linkage Disequilibrium summary for geographic populations arranged by abundance after clone-correction by a hierarchy of Region/Source/Host/Year. 
Pop = Population, N = number of individuals (number of MLG in parentheses), 
eMLG = expected number of MLGs based on rarefaction at min(10, N) individuals (standard error in parentheses), 
H = Shannon-Weiner Index, G = Stoddardt and Taylor's Index, 
$\lambda$ = Simpson's Index, 
*h* = Nei's 1978 gene diversity, 
$I_A$ = the index of association, 
$\bar{r}_d$ = standardized index of association. 
P-value symbols: \* = 0.001, ~ = $\leq 0.05$.
